---
title: "Reproducible Data Analysis and Publishing in Chemistry with R: Creating a workshop experience during the ACS National Meeting"
author: "Donna Wrublewski"
date: "4/24/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary

At the Fall 2019 American Chemical Society National Meeting, two chemistry librarians partnered with a chemistry faculty member to offer a hands-on computer programming workshop. The workshop used the R programming environment and was structured for beginners with no previous experience with it. Three main topics were covered during the five-hour session: introduction to R, working with QSAR data, and creating a report using R Markdown. This report will cover the workshop’s logistics, instructional design and content, and discuss feedback received from participants. Suggestions for future improvements will also be discussed.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

